### 2017-03-18 papers.tex
papers.tex: Improve spacing around alien language boxes
Add fixed version of 2017 paper 62 and list in master ToC
Add newly-received 2017 paper 92 and list in master ToC

\addtrack{Rototiller track}{Special Offers}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{0cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{0cm}
	{}

\addtrack{Lamb track}{It's Only a Game Theory}
\addpaper
	{Dr.\ Boozehead, or How I learned to stop worrying and get drunk: Design principles and analysis of drinking games in the silicon age}
	{Kelvin M.\ Liu-Huang and Emily J.\ Simon}
	{}
	{SIGBOVIK_2017_paper_79}
	{0cm}
	{}
\addpaper
	{A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{}
	{SIGBOVIK_2017_paper_63}
	{0cm}
	{}

@@

\addtrack{Garbage track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ and $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{0cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{0cm}
	{}

>>>>

\addtrack{Rototiller track}{Who Said Money Can't Buy...}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{0cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{0cm}
	{}
\addpaper
	{Grant proposal: Monetary policy of sparkly things}
	{Pete, Luna, and Stefan Muller}
	{}
	{SIGBOVIK_2017_paper_62}
	{0cm}
	{}

\addtrack{Lamb track}{It's Only a Game Theory}
\addpaper
	{Is it Percival time yet?: A preliminary analysis of Avalon gameplay and strategy}
	{Yuzuko Nakamura}
	{}
	{SIGBOVIK_2017_paper_92}
	{0cm}
	{}
\addpaper
	{Dr.\ Boozehead, or How I learned to stop worrying and get drunk: Design principles and analysis of drinking games in the silicon age}
	{Kelvin M.\ Liu-Huang and Emily J.\ Simon}
	{}
	{SIGBOVIK_2017_paper_79}
	{0cm}
	{}
\addpaper
	{A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{}
	{SIGBOVIK_2017_paper_63}
	{0cm}
	{}

@@

\addtrack{Garbage track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad and\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$\quad $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{0cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{0cm}
	{}
